\documentclass[11pt, a4paper]{article}
% --- ATS/Recruiter Friendly Preamble ---
\usepackage[T1]{fontenc}
\usepackage[a4paper, top=1.2cm, bottom=1.2cm, left=1.5cm, right=1.5cm]{geometry}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}   % << NO blue borders, NO colors
\usepackage{enumitem}
\pagestyle{empty}
% Section formatting
\titlespacing*{\section}{0pt}{1ex}{0.8ex}
\titleformat{\section}{\large\bfseries\raggedright}{}{0em}{}
\titlespacing{\section}{0pt}{8pt}{4pt}
\setlength{\parindent}{0pt}
% Section divider
\newcommand{\divider}{\vspace{0.05cm}\hrule\vspace{0.05cm}}
% Custom Project/Experience Item
\newcommand{\cvitem}[3]{%
  \vspace{0.05in}
  \textbf{#1} \hfill \footnotesize{#2}\\
  \textit{#3}\vspace{0.05in}
}
\begin{document}
% =================================
% HEADER
% =================================
\begin{center}
    \fontsize{24pt}{28pt}\selectfont \textbf{SAHIL SHARMA} \\
\end{center}
\vspace{-0.1cm}
\begin{center}
    \footnotesize
    \textbf{Ph:} 7017340383 \textbar\ 
    \textbf{Email:} worksahilsharma@gmail.com \textbar\
    \textbf{LinkedIn:} \href{https://www.linkedin.com/in/sahil-sharma-5a3715270/}{/in/sahil-sharma-5a3715270} \textbar\
    \textbf{GitHub:} \href{https://github.com/shanu133}{/shanu133} \textbar\ 
    Dehradun, Uttarakhand
\end{center}
\divider
% =================================
% PROFESSIONAL SUMMARY
% =================================
\section*{PROFESSIONAL SUMMARY}
Final-year Computer Science student specializing in full-stack web development with hands-on experience building production-ready applications. Proficient in modern JavaScript frameworks, database design, and cloud deployment. Active contributor to open-source communities and experienced in leading technical projects from conception to deployment.
% =================================
% TECHNICAL SKILLS (FIXED – NO OVERFLOW)
% =================================
\section*{TECHNICAL SKILLS}
\begin{tabular}{@{}p{3.3cm} p{12cm}@{}}
\textbf{Languages} & TypeScript, JavaScript, Python (FastAPI), SQL (PostgreSQL), Java \\[3pt]
\textbf{Frameworks} & React.js, Next.js, Tailwind CSS, Framer Motion, Supabase \\[3pt]
\textbf{Cloud/DevOps} & Google Cloud Platform, Vercel, Railway, Git/GitHub, CI/CD Pipelines \\[3pt]
\textbf{Core Concepts} & RESTful APIs, Database Security (RLS), OAuth 2.0, Progressive Web Apps (PWA) \\
\end{tabular}
\vspace{-0.5em}
% =================================
% PROJECTS
% =================================
\section*{DEVELOPMENT PROJECTS}
\cvitem{Stash - Music Discovery Platform}{Founder \& Lead Developer}{React.js, TypeScript, Supabase, FastAPI, Spotify API}
\begin{itemize}
    \item Developed a Progressive Web App (PWA) enabling users to identify and save songs from social media platforms (Instagram, TikTok) directly to their Spotify library, streamlining music discovery workflow.
    \item Implemented robust error handling and retry logic in the data persistence layer using PostgreSQL and Supabase, reducing data loss incidents to zero during production testing.
    \item Built a scalable REST API backend using FastAPI with rate limiting and CORS configuration, deployed on Railway with automated health checks and monitoring.
    \item Applied Row Level Security (RLS) policies in PostgreSQL to enforce strict data isolation, ensuring each user can only access their own saved songs and preferences.
    \item Designed responsive UI components using React.js, Tailwind CSS, and Framer Motion, achieving cross-device compatibility and smooth animations for enhanced user experience.
\end{itemize}
\cvitem{ChaiPaani - Expense Splitting Web App}{Full-Stack Development}{React.js, Supabase, PostgreSQL, Google OAuth}
\begin{itemize}
    \item Built a full-stack expense management application using React.js and Tailwind CSS with real-time balance calculation and group expense tracking features.
    \item Designed normalized PostgreSQL database schema and implemented Row Level Security (RLS) policies in Supabase to ensure transaction privacy and data isolation between user groups.
    \item Integrated Google OAuth 2.0 for secure user authentication and session management.
    \item Deployed application on Vercel with automated CI/CD pipeline for continuous integration and deployment.
\end{itemize}
% =================================
% EDUCATION
% =================================
\section*{EDUCATION}
\begin{itemize}
    \item \textbf{B.Tech. - Computer Science \& Engineering (Full Stack and DevOps)} \hfill 2022--2026
    \item DIT University, Dehradun
\end{itemize}
% =================================
% LEADERSHIP & COMMUNITY
% =================================
\section*{LEADERSHIP \& COMMUNITY}
\cvitem{Co-Organizer}{FOSS Dehradun}{Open-Source Community Management}
\begin{itemize}
    \item Co-founded and organized FOSS Dehradun community meetups, workshops, and technical sessions for 100+ developers.
    \item Promoted open-source collaboration and knowledge sharing within the local developer community.
\end{itemize}
\cvitem{Design Head}{Clickrrati Literrati, University Club}{Creative Leadership}
\begin{itemize}
    \item Led a design team to create visual branding and digital campaigns for college events.
    \item Managed cross-functional collaboration between design, marketing, and event teams.
\end{itemize}
% =================================
% CERTIFICATIONS
% =================================
\section*{CERTIFICATIONS}
\begin{itemize}
    \item Build and Secure Networks in Google Cloud
    \item Introduction to Large Language Models
    \item Google Cloud Digital Leader Training
\end{itemize}
\end{document}
